Loop

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

---
authors:
  - Susanne RK Zajitschek
  - Felix Zajitschek
  - Russell Bonduriansky
  - Robert C Brooks
  - Will Cornwell
  - Daniel S Falster
  - Malgorzata Lagisz
  - Jeremy Mason
  - Alistair M Senior
  - Daniel WA Noble
  - Shinichi Nakagawa
  - Evolution & Ecology Research Center, School of Biological, Earth, and Environmental Sciences, University of New South Wales, Sydney, Australia; 
  - Liverpool John Moores University, School of Biological and Environmental Sciences, Liverpool, United Kingdom; 
  - European Bioinformatics Institute (EMBL- EBI), European Molecular Biology Laboratory, Wellcome Trust Genome Campus, Hinxton, United Kingdom; 
  - University of Sydney, Charles Perkins Centre, School of Life and Environmental Sciences, School of Mathematics and Statistics, Sydney, Australia; 
  - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia
---

@@

## Introduction
Sex differences arise because selection acts on the two sexes differently, especially on traits associated with mating and reproduction (Darwin, 1871). Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist. However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016). Therefore, many (bio-)medical studies have only been conducted with male subjects. Consequently, our knowledge is biased. For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (Nowogrodzki, 2017). This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (Zucker and Prendergast, 2020). Only recently have (bio-)medical scientists started considering sex differences in their research (Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018). Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a). 
When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances). Despite this, two hypotheses exist that explain why trait variability might be expected to differ between the sexes. Interestingly, these two hypotheses make opposing predictions.

 this stupid figure has to get embedded    
 ![Fig1](./Figures/Figure1.png)

@@

 ![Fig2](./Figures/Figure2.png)

@@

@@

 ![Fig3](./Figures/Figure3.png)

@@

```{r packages1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
library(pacman)
pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
data <- readRDS(here("export", "data_clean.rds")) 
procedures <- read_csv(here("data", "procedures.csv"))

n <- length(unique(data$id))
# Create dataframe to store results
results_alltraits_grouping <- 
    data.frame(tibble(id = 1:n, 
           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, lnCVR_I2=0,
            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, lnVR_I2=0,
            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, lnRR_I2=0,
           k=0, trait=0, male_N = 0, female_N=0, min_male_N = 0, max_male_N = 0, mean_male_N = 0,
              min_female_N = 0, max_female_N = 0, mean_female_N = 0))
for (t in 1:n) {
  tryCatch(
    {
      results <- data %>%
                 data_subset_parameterid_individual_by_age(t) %>%
                 calculate_population_stats()                 %>%
                 create_meta_analysis_effect_sizes()          %>%
                 mutate(err = seq_len(n()))
      # lnCVR,  log repsonse-ratio of the coefficient of variance
      cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
                             random = list(~ 1 | strain_name, 
                                           ~ 1 | production_center, 
                                           ~ 1 | err), 
                             control = list(optimizer = "optim", 
                                            optmethod = "Nelder-Mead", 
                                            maxit = 1000), 
                             verbose = F, data = results)

@@

  # Create summary of number of parameter names in each parameter group, and merge back together
meta1b <-
  meta1 %>%
  group_by(parameter_group) %>% 
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]
# Create subsets with > 1 count (par_group_size > 1) 
           meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
meta1_sub$sampleSize <- as.numeric(meta1_sub$k)
# Nesting and meta-analyses on correlated traits, using robumeta
n_count <- meta1_sub %>%
           group_by(parameter_group) %>%
           mutate(raw_N = sum(sampleSize)) %>%
           nest() %>%
           ungroup()
model_count <- n_count %>%
  mutate(
     model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,  data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnRR_se)^2)),
     model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,  data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnVR_se)^2)),
    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnCVR_se)^2))
  )
#### Extracting and save parameter estimates
# Here we apply an additional function to collect the outcomes of the 'mini-meta-analysis' that has condensed our non-independent traits. Values from our second-order meta-analysis using robu-meta are then extracted
count_fun <- function(mod_sub) {
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))
} # estimate, lower ci, upper ci, SE

# Extraction of values created during meta-analyses using robumeta
robusub_RR <- model_count %>%
              transmute(parameter_group, 
                        estimatelnRR = map(model_lnRR, count_fun)) %>%
              mutate(r = map(estimatelnRR, 
                             ~ data.frame(t(.)))) %>%
              unnest(r) %>%
              select(-estimatelnRR) %>%
              purrr::set_names(c("parameter_group", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"))
robusub_CVR <- model_count %>%
               transmute(parameter_group, 
                         estimatelnCVR = map(model_lnCVR, count_fun)) %>%
               mutate(r = map(estimatelnCVR, 
                              ~ data.frame(t(.)))) %>%
               unnest(r) %>%
               select(-estimatelnCVR) %>%
               purrr::set_names(c("parameter_group", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se"))
robusub_VR <- model_count %>%
              transmute(parameter_group, 
                        estimatelnVR = map(model_lnVR, count_fun)) %>%
              mutate(r = map(estimatelnVR, 
                             ~ data.frame(t(.)))) %>%
              unnest(r) %>%
              select(-estimatelnVR) %>%
              purrr::set_names(c("parameter_group", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se"))
robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
#### Combining data 
# Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
meta_all <- meta1 %>%
            filter(par_group_size == 1) %>%
            as_tibble()
# Step 1:  Columns are matched by name (in our case, 'parameter_group'), and any missing columns will be filled with NA
  combinedmeta <- bind_rows(robu_all, meta_all)
# glimpse(combinedmeta)
# Steps 2&3: Add information about number of traits in a parameter group, procedure, and grouping term
              metacombo <- combinedmeta
       metacombo$counts <- meta1$par_group_size[match(metacombo$parameter_group, meta1$parameter_group)] 
   metacombo$procedure2 <- meta1$procedure[match(metacombo$parameter_group, meta1$parameter_group)]
metacombo$GroupingTerm2 <- meta1$GroupingTerm[match(metacombo$parameter_group, meta1$parameter_group)]
# Clean-up, reorder, and rename 
metacombo <- metacombo[c("parameter_group", "counts","procedure2","GroupingTerm2", "lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR","lnVR_lower","lnVR_upper","lnVR_se","lnRR","lnRR_lower","lnRR_upper","lnRR_se")] 
   names(metacombo)[names(metacombo)=="procedure2"] <- "procedure" 
names(metacombo)[names(metacombo)=="GroupingTerm2"] <- "GroupingTerm"

@@

blah blah

```{r Fig3, fig.cap = "Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Figure 1.1D. Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure1.1). Both panels represent results evaluated across all traits. Traits that are male biased are shown in blue, whereas female bias data is represented in orange.[Figure 4 in manuscript]"}
Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
Fig4
```

>>>>

---
authors:
  - Susanne RK Zajitschek
  - Felix Zajitschek
  - Russell Bonduriansky
  - Robert C Brooks
  - Will Cornwell
  - Daniel S Falster
  - Malgorzata Lagisz
  - Jeremy Mason
  - Alistair M Senior
  - Daniel WA Noble
  - Shinichi Nakagawa
  - Evolution & Ecology Research Center, School of Biological, Earth, and Environmental Sciences, University of New South Wales, Sydney, Australia; 
  - Liverpool John Moores University, School of Biological and Environmental Sciences, Liverpool, United Kingdom; 
  - European Bioinformatics Institute (EMBL- EBI), European Molecular Biology Laboratory, Wellcome Trust Genome Campus, Hinxton, United Kingdom; 
  - University of Sydney, Charles Perkins Centre, School of Life and Environmental Sciences, School of Mathematics and Statistics, Sydney, Australia; 
  - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia
bibliography: SexDiff.bib
---

@@

## Introduction
Sex differences arise because selection acts on the two sexes differently, especially on traits associated with mating and reproduction (@darwin1871) (Darwin, 1871). Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist. However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (@clayton2016; @flanagan2014; @karp2017; @klein2015; @prendergast2014; @shansky2016) (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016). Therefore, many (bio-)medical studies have only been conducted with male subjects. Consequently, our knowledge is biased. For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (@nowogrodzki2017)(Nowogrodzki, 2017). This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (@zucker2020) (Zucker and Prendergast, 2020). Only recently have (bio-)medical scientists started considering sex differences in their research (@dorris2015; @ingvorsen2017; @robinson2017; @smarr2017; @ahmad2017; @foltin2018; @thompson2018)(Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018). Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (@clayton2016; @clayton2014; @nih2015a) (NIH, 2015a(Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a). 
When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances). Despite this, two hypotheses exist that explain why trait variability might be expected to differ between the sexes. Interestingly, these two hypotheses make opposing predictions.

## Figure 1
 ![Fig1](./Figures/Figure1.png)

### Overview of meta-analytic methods used to detect differences in means and variances in any given trait (e.g. body size in mice).
The orange shading represents females (F), turquoise shading stands for males (M). The solid circle represents a mean trait value within the respective group. Solid lines represent standard deviation, with upper and lower bounds indicated by diamond shapes. Below, we present three types of effect sizes that can be used for comparing two groups, along with the respective formulas and interpretations. Compared to lnVR (the ratio of SD), lnCVR (the ratio of CV or relative variance) provides a more general measure of the difference in variability between two groups (mean-adjusted variability ratio).

 ## Figure 1—figure supplement 1 
 this code doesn't make sense here - as it needs all the code that's introduced later
 ```{r FigCor, fig.height=3, message = FALSE, fig.cap= "Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B).[Figure 1-figure supplement 1 in manuscript]"}
# First, clean up the data
 results <- data %>%
            group_by(population,
             production_center,  
             strain_name,  
             parameter_name,
             sex) %>%
    summarise(trait  = parameter_name[1],
              x_bar  = mean(data_point, na.rm = TRUE),
              x_sd   =   sd(data_point, na.rm = TRUE),
              n_ind  = n()) %>%
    ungroup() %>%
    filter(n_ind > 5) %>%   # NOTE here that you are excluding data with 5 exactly....
    group_by(population) %>%
    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
    multi_spread(sex, c(x_bar, x_sd, n_ind)) %>%
    mutate(lnMean_m = log(male_x_bar),
           logSD_m  = log(male_x_sd),
           lnMean_f = log(female_x_bar),
           lnSD_f   = log(female_x_sd)) %>%
    filter(!is.na(logSD_m) & !is.inf(logSD_m)) %>%
    filter(!is.na(lnSD_f) & !is.inf(lnSD_f))

male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
    geom_point(color = "#66C2A5", size = 2) +
   geom_smooth(method = "lm", se = FALSE, color="black") + 
    labs(x = "log (Mean)",
         y = "log (SD)") + 
    theme_classic()
female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
    geom_point(color = "#FC8D62", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color="black")+
    labs(x = "log (Mean)",
         y = "log (SD)") + 
    theme_classic()
ggarrange(male, female, ncol = 2, nrow = 1, labels = c("A", "B"))
```
 ![Fig1sup](./Figures/Figure1sup.png)

 ### Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B).

@@

## Figure 2
 ![Fig2](./Figures/Figure2.png)

## The two hypotheses (‘greater male variability’ versus ‘estrus-mediated variability’) have different predictions on how variabilities influence total observed phenotypic variance (Vtotal in the figure).
For greater male variability, the within-subject (or within-trait) variation Vwithin could be potentially negligible or is equal in males and females. This is illustrated as the shaded distributions around each individual mean (dashed vertical lines), which are of equal area for the males (turquoise) and females (orange). The greater value of Vtotal is driven by wider distribution of mean trait values in males compared to females (i.e. Vbetween, represented by a thick horizontal bar). The estrus-mediated variability hypothesis, in contrast, assumes that within-subject [or within-trait] variability is much higher in females than in males (broader orange-shaded trait distributions than turquoise distributions), while the variability of the means between individuals stays the same (thick horizontal bars).

@@

## Figure 3
 ![Fig3](./Figures/Figure3.png)

### Workflow of data processing and meta-analysis.

@@

@@

```{r packages1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
library(readr)
library(dplyr)
library(devtools)
library(purrr)
library(tidyverse)
library(tidyr)
library(tibble)
library(kableExtra)
library(ggpubr)
library(ggplot2)
library(png)
library(grid)
library(splus2R)

# missing for meta-analysis: metafor, robumeta
# pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
```
Loading data & functions
```{r}
data <- readRDS(github://itchyshin/mice_sex_diff/export/data_clean.rds) 
procedures <- read_csv(github://itchyshin/mice_sex_diff/export/procedures.csv)
n <- length(unique(data$id))

# loads the raw data, setting some default types for various columns
load_raw <- function(filename) {
  read_csv(filename,
    col_types = cols(
      .default = col_character(),
      project_id = col_character(),
      id = col_character(),
      parameter_id = col_character(),
      age_in_days = col_integer(),
      date_of_experiment = col_datetime(format = ""),
      weight = col_double(),
      phenotyping_center_id = col_character(),
      production_center_id = col_character(),
      weight_date = col_datetime(format = ""),
      date_of_birth = col_datetime(format = ""),
      procedure_id = col_character(),
      pipeline_id = col_character(),
      biological_sample_id = col_character(),
      biological_model_id = col_character(),
      weight_days_old = col_integer(),
      datasource_id = col_character(),
      experiment_id = col_character(),
      data_point = col_double(),
      age_in_weeks = col_integer(),
      `_version_` = col_character()
    )
  )
}
# Apply some standard cleaning to the data
clean_raw_data <- function(mydata) {

  group <- read_csv(here("data", "ParameterGrouping.csv"))

  tmp <- 
    mydata %>%
    # Filter to IMPC source (recommend by Jeremey in email to Susi on 20 Aug 2018)
    filter(datasource_name == "IMPC") %>%

# standardise trait names
    mutate(parameter_name = tolower(parameter_name)) %>%
    # remove extreme ages
    filter(age_in_days > 0 & age_in_days < 500) %>%
    # remove NAs
    filter(!is.na(data_point)) %>%
    # subset to reasonable set of variables, date_of_experiment used as an indicator of batch-level effects
    select(production_center, 
           strain_name, 
           strain_accession_id, 
           biological_sample_id, 
           pipeline_stable_id, 
           procedure_group, 
           procedure_name, 
           sex, 
           date_of_experiment, 
           age_in_days, 
           weight, 
           parameter_name, 
           data_point) %>% 
    # sort
    arrange(production_center, biological_sample_id, age_in_days)

    # filter to groups with > 1 centre  
    merge(tmp, 
          tmp %>% group_by(parameter_name) %>%
    summarise(center_per_trait = length(unique(production_center, na.rm = TRUE)))
        )%>%
    filter(center_per_trait >= 2) %>% 
    # Define population variable
    mutate(population = sprintf("%s-%s", production_center, strain_name)) %>% 
    # add grouping variable: these were decided based on functional groups and procedures 
    mutate(parameter_group = group$parameter[match(parameter_name, group$parameter_name)] ) %>%

    # Assign unique IDs (per trait)
    # each unique parameter_name (=trait,use trait variable) gets a unique number ('id')
    # We add a new variable, where redundant traits are combined
    #[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]
    mutate(id = match(parameter_name, unique(parameter_name))) %>% 
    as_tibble()
    }

    data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
  tmp <- mydata %>%
    filter(age_in_days >= age_min,
           id == parameter) %>%
  # Take results for single individual closest to age_center
    mutate(age_diff = abs(age_center - age_in_days)) %>%
    group_by(biological_sample_id) %>%
    filter(age_diff == min(age_diff)) %>%
    select(-age_diff)

  # Still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
  tmp[j, ] 
  }

  # Function re-organises the data so that the male and female data are side-by-side as columns to make effect size calculations easier.
multi_spread <- function(df, key, value) {
    # quote key
      keyq <- rlang::enquo(key)
    # break value vector into quotes
    valueq <- rlang::enquo(value)
         s <- rlang::quos(!!valueq)

         df                           %>% 
        gather(variable, value, !!!s) %>%
        unite(temp, !!keyq, variable) %>%
        spread(temp, value)
}
# Function will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format making it ready for effect size calculations
calculate_population_stats <- function(mydata, min_individuals = 5){
    mydata %>% 
    group_by(population,
             production_center,  
             strain_name,  
             sex) %>%
    summarise(trait  = parameter_name[1],
              x_bar  = mean(data_point, na.rm = TRUE),
              x_sd   =   sd(data_point, na.rm = TRUE),
              n_ind  = n()) %>%
    ungroup() %>%
    filter(n_ind > min_individuals) %>%   
    group_by(population) %>%
    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
    multi_spread(sex, c(x_bar, x_sd, n_ind))      # Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data
}

#This function takes the data and computes lnCVR, lnVR and ROM (lnRR) using male and female data to generate effect size statistics for meta-analyses
create_meta_analysis_effect_sizes <- function(mydata, measure = c("CVR", "VR", "ROM")){
  for(i in 1:length(measure)){
    mydata <- metafor::escalc(m1i  = male_x_bar, 
                              m2i  = female_x_bar, 
                              sd1i = male_x_sd, 
                              sd2i = female_x_sd, 
                              n1i  = male_n_ind, 
                              n2i  = female_n_ind, 
                              data = mydata, 
                           measure = measure[i], 
                         var.names = c(paste0("effect_size_", measure[i]), 
                                      paste0("sample_variance_", measure[i])),
                            append = TRUE)
    }
    return(mydata)
}

```{r metaanlysis prep, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
# Create dataframe to store results
results_alltraits_grouping <- 
    data.frame(tibble(id = 1:n, 
           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, lnCVR_I2=0,
            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, lnVR_I2=0,
            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, lnRR_I2=0,
           k=0, trait=0, male_N = 0, female_N=0, min_male_N = 0, max_male_N = 0, mean_male_N = 0,
              min_female_N = 0, max_female_N = 0, mean_female_N = 0))
for (t in 1:n) {
  tryCatch(
    {
      results <- data %>%
                 data_subset_parameterid_individual_by_age(t) %>%
                 calculate_population_stats()                 %>%
                 create_meta_analysis_effect_sizes()          %>%
                 mutate(err = seq_len(n()))
      # lnCVR,  log repsonse-ratio of the coefficient of variance
      cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
                             random = list(~ 1 | strain_name, 
                                           ~ 1 | production_center, 
                                           ~ 1 | err), 
                             control = list(optimizer = "optim", 
                                            optmethod = "Nelder-Mead", 
                                            maxit = 1000), 
                             verbose = F, data = results)

@@

  # Create summary of number of parameter names in each parameter group, and merge back together
meta1b <-
  meta1 %>%
  group_by(parameter_group) %>% 
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]
# Create subsets with > 1 count (par_group_size > 1) 
           meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
meta1_sub$sampleSize <- as.numeric(meta1_sub$k)
# Nesting and meta-analyses on correlated traits, using robumeta
n_count <- meta1_sub %>%
           group_by(parameter_group) %>%
           mutate(raw_N = sum(sampleSize)) %>%
           nest() %>%
           ungroup()
model_count <- n_count %>%
  mutate(
     model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,  data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnRR_se)^2)),
     model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,  data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnVR_se)^2)),
    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnCVR_se)^2))
  )
 ```
Additional meta-analyses and preparation for plots

 ```{r extracting estimates}
#### Extracting and save parameter estimates
# Here we apply an additional function to collect the outcomes of the 'mini-meta-analysis' that has condensed our non-independent traits. Values from our second-order meta-analysis using robu-meta are then extracted
count_fun <- function(mod_sub) {
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))
} # estimate, lower ci, upper ci, SE

# Extraction of values created during meta-analyses using robumeta
robusub_RR <- model_count %>%
              transmute(parameter_group, 
                        estimatelnRR = map(model_lnRR, count_fun)) %>%
              mutate(r = map(estimatelnRR, 
                             ~ data.frame(t(.)))) %>%
              unnest(r) %>%
              select(-estimatelnRR) %>%
              purrr::set_names(c("parameter_group", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"))
robusub_CVR <- model_count %>%
               transmute(parameter_group, 
                         estimatelnCVR = map(model_lnCVR, count_fun)) %>%
               mutate(r = map(estimatelnCVR, 
                              ~ data.frame(t(.)))) %>%
               unnest(r) %>%
               select(-estimatelnCVR) %>%
               purrr::set_names(c("parameter_group", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se"))
robusub_VR <- model_count %>%
              transmute(parameter_group, 
                        estimatelnVR = map(model_lnVR, count_fun)) %>%
              mutate(r = map(estimatelnVR, 
                             ~ data.frame(t(.)))) %>%
              unnest(r) %>%
              select(-estimatelnVR) %>%
              purrr::set_names(c("parameter_group", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se"))
robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)

#### Combining data 
# Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
meta_all <- meta1 %>%
            filter(par_group_size == 1) %>%
            as_tibble()
# Step 1:  Columns are matched by name (in our case, 'parameter_group'), and any missing columns will be filled with NA
  combinedmeta <- bind_rows(robu_all, meta_all)
# glimpse(combinedmeta)
# Steps 2&3: Add information about number of traits in a parameter group, procedure, and grouping term
              metacombo <- combinedmeta
       metacombo$counts <- meta1$par_group_size[match(metacombo$parameter_group, meta1$parameter_group)] 
   metacombo$procedure2 <- meta1$procedure[match(metacombo$parameter_group, meta1$parameter_group)]
metacombo$GroupingTerm2 <- meta1$GroupingTerm[match(metacombo$parameter_group, meta1$parameter_group)]
# Clean-up, reorder, and rename 
metacombo <- metacombo[c("parameter_group", "counts","procedure2","GroupingTerm2", "lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR","lnVR_lower","lnVR_upper","lnVR_se","lnRR","lnRR_lower","lnRR_upper","lnRR_se")] 
   names(metacombo)[names(metacombo)=="procedure2"] <- "procedure" 
names(metacombo)[names(metacombo)=="GroupingTerm2"] <- "GroupingTerm"

@@

## Figure 4

```{r  fig.cap = "Sex bias in trait groups.
Panel (A) shows the numbers of traits that are either male-biased (turquoise) or female-biased (orange) across functional groups. The x-axes in Panel A represents the overall percentages of traits with a given direction of sex bias: orange shading when meta-analytic mean < 0 (female-biased), turquoise shading when meta-analytic mean > 0 (male-biased). White numbers inside the turquoise bars represent numbers of traits that show male bias within a given group of traits, numbers inside the orange bars represent the number of female-biased traits. Panel (B) shows effect sizes and 95% CI from separate meta-analysis for each functional group (Figure 3H). Traits that are male-biased in Panel B are shifted towards the righthand side of the zero-midline (near the turquoise male symbol), whereas female-biased traits are shifted towards the left (near the orange female symbol)."}

Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
Fig4
```
## Figure 4—figure supplement 1
```{r code for heterogeneity}
### Preparing heterogeneity
# Create dataframe to store results
results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 30), ncol = 30)))
names(results.allhetero.grouping) <- c(
  "id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR",
  "s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR",
  "s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR",
  "s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper",
  "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"
)

#Loop
for (t in 1:n) {
  tryCatch(
    {
      results <- data %>% 
                  data_subset_parameterid_individual_by_age(t) %>% 
                  calculate_population_stats() %>% 
                  create_meta_analysis_effect_sizes() %>%
                  mutate(err = seq_len(n()))

      # lnCVR, logaritm of the ratio of male and female coefficients of variance
      cvr. <- metafor::rma.mv(yi = effect_size_CVR, 
                              V = sample_variance_CVR, 
                              random = list(~ 1 | strain_name, ~ 1 | production_center,~ 1 | err), 
                              control = list(optimizer = "optim", 
                                             optmethod = "Nelder-Mead", 
                                             maxit = 1000), 
                              data = results)

      results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
      results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
      results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
      results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
      results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
      results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
      results.allhetero.grouping[t, 20] <- cvr.$b
      results.allhetero.grouping[t, 21] <- cvr.$ci.lb
      results.allhetero.grouping[t, 22] <- cvr.$ci.ub
      results.allhetero.grouping[t, 23] <- cvr.$se

       # lnVR, male to female variability ratio (logarithm of male and female standard deviations)
      vr. <- metafor::rma.mv(yi = effect_size_VR, 
                             V = sample_variance_VR, 
                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
                             control = list(optimizer = "optim", 
                                            optmethod = "Nelder-Mead", 
                                            maxit = 1000), 
                             data = results)

      results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
      results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
      results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
      results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
      results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
      results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
      results.allhetero.grouping[t, 24] <- vr.$b
      results.allhetero.grouping[t, 25] <- vr.$ci.lb
      results.allhetero.grouping[t, 26] <- vr.$ci.ub
      results.allhetero.grouping[t, 27] <- vr.$se
      # lnRR, response ratio (logarithm of male and female means)
      rr. <- metafor::rma.mv(yi = effect_size_ROM, 
                             V = sample_variance_ROM, 
                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
                             control = list(optimizer = "optim", 
                                            optmethod = "Nelder-Mead", 
                                            maxit = 1000), 
                             data = results)

      results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
      results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
      results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
      results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
      results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
      results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
      results.allhetero.grouping[t, 28] <- rr.$b
      results.allhetero.grouping[t, 29] <- rr.$ci.lb
      results.allhetero.grouping[t, 30] <- rr.$ci.ub
      results.allhetero.grouping[t, 31] <- rr.$se
    },
    error = function(e) {
      cat("ERROR :", conditionMessage(e), "\n")
    }
     )
}
